YilunZhuCode

### 2024-04-17 Draft_report.Rmd
Yilun upload code for decompose, MK test, ADF test SSES,NN, ArimaFourier, and socres

```{r, echo=FALSE}
library(ggplot2)
library(readxl)
library(cowplot)
library(tidyverse)
library(lubridate)
library(dplyr)
library(knitr)
library(caret)
library(forecast)
library(zoo)
```

@@

HERE WE SHOULD DECOMPOSE THE DATA.

@@

**Description**
1. SARIMA model
2. TBATS model
3. ETS model
4. SSES model
5. NN

@@

```{r}
forecast_accuracySarima <- accuracy(sarima_forecast, test_ts)
print(forecast_accuracySarima)
```

@@

```{r}
stlf_accuracy <- accuracy(ETS_for, test_ts)
print(stlf_accuracy)
```

@@

```
```{r}
TBATS_accuracy <- accuracy(TBATS_for, test_ts)
print(TBATS_accuracy)
```

>>>>

```{r, echo=FALSE}
library(ggplot2)
library(readxl)
library(cowplot)
library(tidyverse)
library(lubridate)
library(dplyr)
library(knitr)
library(caret)
library(forecast)
library(zoo)
library(Kendall)
library(tseries)
library(outliers)
library(smooth)
```

@@

HERE WE SHOULD DECOMPOSE THE DATA.
```{r}
decomposed_Temperature <- decompose(temperature_ts, type = "additive")
plot(decomposed_Temperature)

#Testing if the trend is stationary
MKTest <- MannKendall(temperature_ts)
print(summary(MKTest))

print(adf.test(temperature_ts, alternative = "stationary"))
```

@@

**Description**
1. SARIMA model
2. Arima+Fourier
3. TBATS model
4. ETS model
5. SSES model
6. Neural Network

@@

```{r}
forecast_accuracySarima <- accuracy(sarima_forecast)
print(forecast_accuracySarima)
```

*ARIMA+fourier Modeling*
```{r ARIMA, echo=TRUE, message=FALSE, warning=FALSE}
ARIMA_Four_fit <- auto.arima(train_ts, 
                             seasonal=TRUE, 
                             lambda=0,
                             xreg=fourier(train_ts, 
                                          K=c(6))
                             )

ARIMA_Four_for <- forecast(ARIMA_Four_fit,
                           xreg=fourier(train_ts,
                                        K=c(6),
                                        h=h),
                           h=h
                           )

autoplot(ARIMA_Four_for) + ylab("Temperature")

autoplot(temperature_ts) +
  autolayer(ARIMA_Four_fit$fitted, series="ARIMA_FOURIER Fitted",PI=FALSE) +
  autolayer(ARIMA_Four_for, series="ARIMA_FOURIER Forecast",PI=FALSE) +
  ylab("Temperature")

checkresiduals(ARIMA_Four_for)

forecast_accuracyARIMA_Four <- accuracy(ARIMA_Four_for)
print(forecast_accuracyARIMA_Four)
```

@@

```{r}
stlf_accuracy <- accuracy(ETS_for)
print(stlf_accuracy)
```

@@

```
```{r}
TBATS_accuracy <- accuracy(TBATS_for)
print(TBATS_accuracy)
```

*SSES*
```{r, echo=FALSE}
SSES_seas <- es(train_ts,model="ZZZ", h= h,holdout=FALSE)
plot(SSES_seas)
checkresiduals(SSES_seas)

#Plot model + observed data
autoplot(temperature_ts) +
  autolayer(SSES_seas$fitted, series="SSES Fit",PI=FALSE)+
  autolayer(SSES_seas$forecast, series="SSES Forecast",PI=FALSE)+
  ylab("Temperature")

forecast_accuracy_SSES <- accuracy(SSES_seas)
```

*Neural Network*
```{r}
NN_fit <- nnetar(train_ts,
                 p=1,
                 P=1,
                 xreg=fourier(train_ts, K=c(6)))

NN_for <- forecast(NN_fit, h= h,xreg=fourier(train_ts, 
                                          K=c(6),h= h))

autoplot(NN_for) +
  ylab("Temperature C")

autoplot(test_ts) +
  autolayer(NN_for, series="Neural Network",PI=FALSE)+
  ylab("Temperature")

autoplot(temperature_ts) +
  autolayer(NN_for$fitted, series="NN fit",PI=FALSE) +
  autolayer(NN_for$mean, series="NN forecast",PI=FALSE)+
  ylab("Temperature")

checkresiduals(NN_fit)

forecast_accuracy_NN <- accuracy(NN_for)
```
*Create Scores*
```{r}

#Model 1: Sarima
Sarima_scores <- accuracy(sarima_forecast$mean, test_ts)

#Model 2: ARIMA + Fourier
ArimaFour_scores <- accuracy(ARIMA_Four_for$mean, test_ts)

#Model 3: ETS+STL 
stlf_scores <- accuracy(ETS_for$mean, test_ts)

# Model 4:  TBATS 
TBATS_scores <- accuracy(TBATS_for$mean, test_ts)

# Model 5:  SSES 
SSES_scores <- accuracy(NN_for$mean, test_ts)

# Model 6:  Neural Network 
NN_scores <- accuracy(SSES_seas$forecast, test_ts)

*Create Score table*
```{r}
scores <- as.data.frame(
  rbind(Sarima_scores, ArimaFour_scores, stlf_scores, TBATS_scores, SSES_scores, NN_scores)
  )
row.names(scores) <- c("Sarima", "ARIMA+Fourier","ETS+STL","TBATS","SSES", "NN")

best_model_index <- which.min(scores[,"RMSE"])
cat("The best model by RMSE is:", row.names(scores[best_model_index,]))                       
```

### 2024-04-17 Yilun Upload/YilunCode.Rmd
Yilun upload code for decompose, MK test, ADF test SSES,NN, ArimaFourier, and socres

#create a subset for testing purpose
ts_Temperature_Monthly_test <- subset(ts_Temperature_Monthly,
                                   start = length(ts_Temperature_Monthly)-n_for)

MKTest <- MannKendall(ts_Temperature_Monthly)
print(summary(MKTest))

>>>>

#create a subset for testing purpose
ts_Temperature_Monthly_test <- subset(ts_Temperature_Monthly,
                                   start = length(ts_Temperature_Monthly)-n_for)
#Testing if the trend is stationary
MKTest <- MannKendall(ts_Temperature_Monthly)
print(summary(MKTest))
